MinCall --- MinION basecaller model pogonjen dubokim učenjem

### 2017-05-14 paper/main.tex
Fix and first draft is kinda ready

Finally, I'm thanking various other people whose code, tools and advice I've used in completing this paper: Fran Jurišić, Ana Marija Selak, and Ivan Sović.

>>>>

Finally, I'm thanking various other people whose code, tools and advice I've used in completing this paper: Fran Jurišić, Ana Marija Selak, Ivan Sović and Martin Šošić.
